Quality Definitions of Qualities

### 2021-10-09 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
added sustainability definitions

>>>>

\begin{defn}
Sustainable Software is software whose direct and indirect negative impacts on economy, society, human beings, and the environment resulting from development, deployment, and usage of the software is minimal and/or has a positive effect on sustainable development \citep{dick2010model}.
\end{defn}

\begin{defn}
The art of developing sustainable software with a sustainable software engineering process so that negative and positive impacts result in and/or are expected to result from the software product over its whole life cycle are continuously assessed, documented, and used for further optimization of the software product \citep{venters2014software}.
\end{defn}
